\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-20 paper/subdocuments/results.Rnw
updated Brülhart data, plot net income vs equivalised net income

% Nicht eher nur CH-Plot?

>>>>

\subsection{Statistical units}

<<setup_data>>=
bd <- read.csv("../../data/data_Schweiz.csv", header=TRUE,sep=";")
bd.long<-reshape(bd,
varying = c("gini_reink","gini_reinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("Gini net income","Gini equivaliced net income"),
direction ="long")
@

<<With and without equivalence scale>>=
library(ggplot2)
ggplot(db[db$Einheit=="Total",], aes(x=Veranlagungsperiode,y=Gini,shape=Type))+
  scale_y_continuous(limits=c(0.18,0.4))+
  scale_x_continuous(limits=c(1982,2012),breaks=number_ticks(10)) +
  geom_point(aes(shape=Type),size=3)+
  geom_line(data=dflong[dflong$kanton=="CH",],aes(linetype=Type))+
  theme_bw()+
  xlab("tax period")
